---
title: "Assignment 1.8"
author: "Your Name"
date: "09/11/2024"
output:
  html_document:
    df_print: paged
subtitle: 'CPSC 292 Section ##'
---

### Collaboration team: 

Record who you've worked on the assignment with here. 


## Assignment 1.8 -- Matrices

```{r setup, include=FALSE}
# Do not alter this section of code!
knitr::opts_chunk$set(echo = TRUE)
```

Write a R code in each chunk (gray space) that provides answers to the following questions. If any questions need direct answers, give them in regular text space (white space).

### Question 1

*Create a 5 by 6 matrix of random numbers using `runif()` to generate data and store it in a variable named my.matrix1. (The function `runif()` pulls pseudorandom numbers from a normal distribution.)*

```{r}

```

### Question 2 

*Create another matrix using a different method with `runif()` to generate data that is 6 by 5 and store it in a variable named my.matrix2. HINT: use cbind() or rbind().*

```{r}

```


### Question 3

*Use functions to find each of these values.* 

  a. *What are the dimensions of your two matrices?* 
  
```{r}

```

  b. *How many rows and columns do each have?* 
  
```{r}

```
  
  c. *How many numbers do each contain?*
  
```{r}

```

### Question 4

*What are the values at column 5 row 3 for each of your two matrices?*

```{r}

```

### Question 5

*The following line of code does not work. Correct the error so that my.matrix4 is a 5 by 11 matrix.*

```{r}
my.matrix4 <- cbin(my.matrix1, my.matrix2)
```

Turn in this RMD file.