---
title: "Assignment 1.10"
author: "Your Name"
date: "09/13/2024"
output:
  html_document:
    df_print: paged
subtitle: 'CPSC 292 Section ##'
---

### Collaboration team: 

Record who you've worked on the assignment with here. 


## Assignment 1.10 -- Data Frames

```{r setup, include=FALSE}
# Do not alter this section of code!
knitr::opts_chunk$set(echo = TRUE)
```

Write a R code in each chunk (gray space) that provides answers to the following questions. If any questions need direct answers, give them in regular text space (white space).

### Question 1

*Create a data frame that has columns with three different data types.*

```{r}

```

### Question 2

*Load the data set chickwts, which is study on chick weights based on feed type.*

```{r}

```

*Use it to answer the following questions:*

  a. *What is the mean weight of all the chicks in the study?*
  
```{r}

```

  b. *How many chicks are in each feed group?* 
  
```{r}

```
  
  c. *Create two separate vectors with all the weights of the chicks in the study and all the feeds in the study.*
  
```{r}

```
  
  d. *Subset the data frame into a new object that represents only the weights of chicks fed on horsebean.*
  
```{r}

```

  d. *Repeat this subsetting into a new object for chicks fed on sunflower.*
  
```{r}

```

### Question 3

*The following line of code does not work. Correct the error so that the code returns the mean weight of chicks fed soybean or linseed feed.*
```{r}
mean(chickwts$weight[chickwts$feed == "soybean" | chickwts$feed == "linseed",])
```

*Explain why your fix works.*

Your answer here. 

Turn in this RMD file.