---
title: "Assignment 1.6"
author: "Your Name"
date: "09/08/2023"
output:
  html_document:
    df_print: paged
subtitle: 'CPSC 292 Section ##'
---

### Collaboration team: 

Record who you've worked on the assignment with here. 


## Assignment 1.6 -- Data Types in R

```{r setup, include=FALSE}
# Do not alter this section of code!
knitr::opts_chunk$set(echo = TRUE)
```

Write a R code in each chunk (gray space) that provides answers to the following questions. If any questions need direct answers, give them in regular text space (white space).

### Question 1

*For the following inputs, list all of the atomic data types that would be appropriate to store data in R. `Appropriate' means that it retains the specific information that someone would want to keep, for example: storing the number 7 as a numeric would keep the value of 7, but storing 7 as a character would not. *

*Code an example for each.*

*Hint: vectors are stored using c()!*


  a. *The word puppy*
  
  List data types here:
  
```{r}

```
  b. *The condition TRUE*
  
  List data types here:
  
```{r}

```
  
  c. *The word h8tr*
  
  List data types here:
  
```{r}

```
  
  d. *The vector < 1, 0, 1, 0 >*
  
  List data types here:
  
```{r}

```
  
  e. *The vector < 9.99, 8.37 >*
  
  List data types here:
  
```{r}

```

  f. *The vector < 9 + 3i, 3i >*
  
  List data types here:

```{r}

```

  g. *The number 16*
  
  List data types here:

```{r}

```

  h. *The number 3.6*

  List data types here:

```{r}

```

### Question 2

*For the following functions, what types of data do they accept as arguments and what data types do they return as values?*

*Code a working example of each.*

*Hint: look up the help documentation for each function!*

 a. `median()`
  
  Your answer here.
  
```{r}

```

 b. `sd()`
 
  Your answer here.
  
```{r}

```
 
 c. `any()`
   
  Your answer here.
  
```{r}

```
 
 d. `cut()`
 
  Your answer here.
  
```{r}

```
 
 e. `order()`
  
  Your answer here.
  
```{r}

```

### Question 3

*Run the function `is.character()` on the coded example for each answer in question 1 (give each example its own line). Explain what the output of these functions mean.*

```{r}

```

Your answer here. 



Turn in this RMD file.
