---
title: "Assignment 1.7"
author: "Your Name"
date: "09/09/2024"
output:
  html_document:
    df_print: paged
subtitle: 'CPSC 292 Section ##'
---

### Collaboration team: 

Record who you've worked on the assignment with here. 


## Assignment 1.7 -- Vectors

```{r setup, include=FALSE}
# Do not alter this section of code!
knitr::opts_chunk$set(echo = TRUE)
```

Write a R code in each chunk (gray space) that provides answers to the following questions. If any questions need direct answers, give them in regular text space (white space).

### Question 1

*Create a vector that is a sequence of numbers between 30 and 54 with the total length of 600.*

*By what amount is each element separated by? Have R calculate this difference in code.*

```{r}

```

### Question 2

*Create a vector that repeats the same sequence of numbers 5 through 8 fifteen times.*

*Write another line of code that repeats these element-wise.*

```{r}

```

### Question 3

*Create a vector q3 that is a sequence of numbers between 1 and 400 that contains numbers spaced by 0.2 in the code chunk below, then answer each of the following parts with code below.*

```{r}

```

  a. *What class is the vector q3?*

```{r}

```

  
  b. *How long is the vector q3?*
  
```{r}

```

  c. *What is the mean value of the vector q3?*
  
```{r}

```

  d. *What value is at position 78 in the vector q3?*
  
```{r}

```

  e. *What is the sum of the numbers in positions 611 through 762 of the vector q3?*
  
```{r}

```

### Question 4

*You have a vector pop1 which has the elements: < 5, 7.3, 2.1, 11 >. You’d like to add the value 1.3 to each element of pop1 to create a new vector pop2. Write code to do this.*

```{r}
pop1 <- c(5, 7.3, 2.1, 11)
```

*Is the way you've added 1.3 to pop1 adding by element or vectorized? How can you tell?*

Your answer here. 

### Question 5

*The following line of code does not work. Correct the error so that a vector is produced.*

```{r}
pop3 <- (3, 4, 7, 1, 3)
```

Turn in this RMD file.
