---
title: "Assignment 2.2"
author: "Your Name"
date: "9/27/2024"
output:
  html_document:
    df_print: paged
subtitle: 'CPSC 292 Section ##'
---

## Assignment 2.2 

```{r, include=TRUE}
# Loading required libraries

```

Download the robo-mussel.csv data file associated with this assignment. This data is from the Helmuth Lab's Robomussel Database, a collection of intertidal temperatures recorded from model mussels, meant to approximate the body temperatures of mussels, a locations along the west coast of North America. Be sure you put this file in the same directory as the Rmd file so that it runs correctly.

Beware though, the dates will be changed in this file is opened in Microsoft Excel! If this happens and produces an error in Question 3, download the csv again.

### Question 1

*a. Using `read.table()`, load the data from this CSV file into R. There should be one skipped line and there is a header to the file. The separator should be a comma.*

```{r}

```

*b. How many observations (rows) and variables (columns) are in this data set?*

```{r}

```


*c. Are the data in each column the appropriate data class? If not, how can you fix that using the read.table() function?*

Each is OK, the timestamp data should probably be a time class but that's hard to do in read.table().

### Question 2

*Clean the data up using the tidy pipe operator and however many commands you need to make the data set easy to work with. Things to consider cleaning would be: removing observations NA values, standardizing column names, and removing empty rows and columns.  Explain each command you are using and why in the Markdown text before or after the cleaning R chunk of code.*


```{r}

```

At the very least, the data set should be passed through `clean_names()` to standardize column names.

### Question 3

*Plotting time stamped data is sort of painful in base graphics, but here is how to step through it. *

*a. Subset the data into a separate object so that it captures only the first 1,000 rows. (Plotting all of it will take too long.)*


```{r}

```

*b. Next, convert the Timestamp column of the data subset into a POSIXct time format, make sure that it overwrites the Timestamp column (example in the RMarkdown file).*

```{r}
# Example code for a data set named mussel.dat:
#mussel.dat$Timestamp <- as.POSIXct(mussel.dat$Timestamp)

```

*c. Then, make a simple plot of two columns against each other using your subset of the data. Be sure to label everything appropriately (make it look nice!)*

The plot needs axes labels and should look reasonable. 

```{r}

```

