---
title: "Assignment 2.4"
author: "Your Name"
date: "10/2/2024"
output:
  html_document:
    df_print: paged
subtitle: 'CPSC 292 Section ##'
---


## Assignment 2.4

```{r, include=TRUE}
# Loading required libraries

```


### Question 1

*Download the EBKB_WaterQualityData_2020084.csv data file in the Assignment/Unit2/data folder. This data set is the Department of the Interior  \href{https://catalog.data.gov/dataset/water-quality-data-41c5e}{https://catalog.data.gov/dataset/water-quality-data-41c5e} and represents water quality values collected by volunteers at the Back Bay National Wildlife Refuge from 1994 to 2020.*

*a. Read data in using `read.csv()`.*

```{r, include=TRUE}

```

*b. Clean the data of any empty columns and rows, standardize column names, convert the site_id column into a factor. Use the `convert_to_date()` function in the janitor package to convert the read_date column into a date.*

```{r, include=TRUE}

```


*c. What are the columns in this data set and what data class are each?*
```{r, include=TRUE}

```
### Question 2

*Has there been a change in dissolved oxygen over time?*

```{r, include=TRUE}

```



### Question 3

*Is there a relationship between dissolved oxygen and water temperature?*

```{r, include=TRUE}

```




### Question 4

*Is there a difference in water pH between sites?*


```{r, include=TRUE}

```

