---
title: "Assignment 3.2"
author: "Your Name"
date: "10/25/2024"
output:
  html_document:
    df_print: paged
subtitle: "CPSC 292 Section ##"
---

## Assignment 3.2 

```{r, include=TRUE}
# Loading required libraries

```

### Question 1

*Complete the following steps:*

 a.  *Create a function that will take an object `x` and return the results of the following calculation: 4x^4  - sin(3x) + 12.*

```{r, include=TRUE}

```

 b. *Use your function to calculate the result of ten random numbers. Store the results in another object.*
 
```{r, include=TRUE}

```

 c. *Does your function perform a vectorized calculation? How do you know?*
 


### Question 2

*Make a function that reports the area of a land mass in the islands data set. The user input should be the name of the land mass. Include a line of code that uses the function as an example.*

```{r, include=TRUE}

```

### Question 3

*Make a function that reports a correlation value between two values in the Harman23.cor covariation matrix. The inputs should be two values in the covariance matrix. Include a line of code that uses the function as an example.*

```{r, include=TRUE}

```

